COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-09-05 main.tex
Add more figures
Discussion of figure 1

In the CJ simulation, there is no secular forcing from Jupiter and so the mean longitudes and mean anomalies are randomly assigned values between 0 and 2$\pi$. The distribution of eccentricities and inclinations of the planetesimals are chosen so that the effects of viscous stirring and gas drag from the solar nebula are in balance. This occurs when eccentricities are described by a Rayleigh distribution with a mode given by equation 12 in \citet{2002ApJ...581..666K}. The inclination distribution is described by this same function, with a mode that is a factor of 2 smaller \citep{1993MNRAS.263..875I}.

@@

We use equation 12 from kokubo and ida 2002 to set initial free eccentricites and inclinations for particles, in equilibrium with gas drag. These would be about twice as big if we instead used vrandom = vesc, which is the point at which grav stirring stops being very effective. Forced eccentricity and varpi set by secular perturbations by Jupiter, as done by Tabeshian and Weigert.

@@

@@

>>>>

In the CJ simulation, there is no secular forcing from Jupiter and so the mean longitudes and mean anomalies are randomly assigned values between 0 and 2$\pi$. The distribution of eccentricities and inclinations of the planetesimals are chosen so that the effects of viscous stirring and gas drag from the solar nebula are in balance. This occurs when eccentricities are described by a Rayleigh distribution with a scale parameter given by equation 12 in \citet{2002ApJ...581..666K}. The inclination distribution is described by this same function, with a scale parameter that is half as large. This is typical for a sufficiently dynamically heated disk of particles in a Kepler potential \citep{1993MNRAS.263..875I}.

@@

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_a.png}
    \caption{Caption goes here.\label{fig:coll_hist_a}}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
    \caption{Caption goes here.\label{fig:coll_hist_r}}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/m_hist.png}
    \caption{Caption goes here.\label{fig:coll_hist_r}}
\end{figure*}

@@

A side-by-side comparison of the final distribution in cylindrical coordinates of planetesimals from the CJ and EJ simulations is shown in figure \ref{fig:rtheta}. Gaps produced by the 3:1, 2:1 and 5:3 MMR with Jupiter are visible in both frames. In the EJ simulation, a gap in the vicinity of the 5:2 MMR is also visible. The non-axisymmetric character of the gaps reflects the fact that the planetesimals in the vicinity of the resonances (especially the 2:1) are having their eccentricities significantly pumped. (I don't think there should be any azimuthal structure to the gaps in the CJ simulation. This is probably a reflection of the fact that we need to run with smaller timesteps.) Although examining the spatial distribution of planetesimals near MMR in debris disks may be a viable way to detect unseen planets, we will not focus on this topic any longer as it has already been covered in detail in other studies \citep{2016ApJ...818..159T, 2018ApJ...857....3T}. It is worth noting, however that the spatial distribution of planetesimals shown in figure \ref{fig:rtheta} appears qualitatively similar to figures 3 and 4 in \citep{2016ApJ...818..159T}.
